Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2019-12-03 lloveras_2020.tex
muchos cambios en figuras

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_awsom_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
\caption{Latitude-longitude location of each leg of type I (in blue), type II (in red) and type III (in green) meeting the criteria listed in Section \ref{trace} traced with DEMT results, at heights $1.105\,\mrsun$, for CR-2082 (left panel) and CR-2208 (right panel).}
\label{rpoint_demt}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_Tm.eps}
\caption{Comparative statistical distributions of (from left to right): the coronal base electron density $N_e(r=1.055\,\mrsun)$, the electron density scale height $\lN$ and the average electron mean temperature $\aTm$, along all field lines traced in the streamer (type I, top panels), the boundary of the streamer (type II, mid panels) and the Coronal Holes (type III, bottom panels). for CR-2082. DEMT results of CR2082 are shown in blue while those of CR2208 in red. In each panel the median $m$ is indicated.}
\label{histos_fulldemt}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2082_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2082_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2208_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up.eps}
\caption{Average fits of $N_e(r)$ and $T_e(r)$ along all field lines of type I (in blue), of type II (in red) and of type III (in green) meeting the criteria listed in Section \ref{trace} for CR-2082 (top panel) and CR-2208 (bottom panel). In solid lines DEMT traced results and in dashed lines AWSoM results.}
\label{perfiles_promedio}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2082_1105.eps}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2208_1105.eps}
\caption{Longitude-averaged of electron density for DEMT (blue) and AWSoM (red) results at $1.105\,\mrsun$. On the left CR2082 and on the right CR2208, the vertical black lines indicates the longitude-averaged latitudes of the open/close magnetic boundaries.}
\label{perf_lon_ne}
\end{center}
\end{figure}

>>>>

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_awsom_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
\caption{Latitude-longitude location of each leg of type 0 (in cyan), type I (in blue), type II (in red) and type III (in green) meeting the criteria listed in Section \ref{trace} traced with DEMT results, at heights $1.105\,\mrsun$, for CR-2082 (left panel) and CR-2208 (right panel).}
\label{rpoint_demt}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2082_fulltriple_gradt.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2208_fulltriple_gradt.eps}
\caption{Histogram of the temperature radial gradient along each leg of type 0 (in cyan), type I (in blue), type II (in red) and type III (in green) meeting the criteria listed in Section \ref{trace} traced with DEMT results, at heights $1.105\,\mrsun$, for CR-2082 (left panel) and CR-2208 (right panel).}
\label{gradt_demt}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_Tm.eps}
\caption{Comparative statistical distributions of (from left to right): the coronal base electron density $N_e(r=1.055\,\mrsun)$, the electron density scale height $\lN$ and the average electron mean temperature $\aTm$, along all field lines traced in the streamer (type 0 - down loops and type I - up loops), the boundary of the streamer (type II, mid panels) and the Coronal Holes (type III, bottom panels). for CR-2082. DEMT results of CR2082 are shown in blue while those of CR2208 in red. In each panel the median $m$ is indicated.}
\label{histos_fulldemt}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2082_1105.eps}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2208_1105.eps}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2082_1105.eps}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2208_1105.eps}
\caption{Longitude-averaged, in both rotations, of electron density (top) and electron temperature (bottom) for DEMT (blue) and AWSoM (red) results at $1.105\,\mrsun$. On the left CR2082 and on the right CR2208, the vertical black lines indicates the longitude-averaged latitudes of the open/close magnetic boundaries.}
\label{perf_lon_ne}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2082_up_short.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2082_up_short.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2208_up_short.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up_short.eps}
\caption{Average fits of $N_e(r)$ and $T_e(r)$ along all field lines of type I (in blue), of type II (in red) and of type III (in green) meeting the criteria listed in Section \ref{trace} for CR-2082 (top panel) and CR-2208 (bottom panel). In solid lines DEMT traced results and in dashed lines AWSoM results.}
\label{perfiles_promedio}
\end{center}
\end{figure}

@@
